Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-01-25 paperIEEE.tex
Add compound result figures
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@95 db7c848b-7755-4df2-b763-8796797afa52
Move large figures after main text
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@96 db7c848b-7755-4df2-b763-8796797afa52
Address FIXMEs
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@97 db7c848b-7755-4df2-b763-8796797afa52

RLE compression has a very low overhead but
% does not compress the data, since it only
merely removes ``blank space'' in the data. The Snappy compression, used as
default in \textsf{Collage}, achieves the same compression ratio as the LZ
variants at a much higher speed. The ZStandard compressor has roughly the same
speed as the LZ variants at the lowest compression level, but provides
significantly better compression. At higher compression levels it can improve
the compression ratio slightly, but at a high cost for the compression speed.

@@

In this section we present how data distribution and synchronization performs in
real-world applications. We extracted the existing data distribution code in a
PLY (eqPly) and a volume renderer (Livre) into a benchmark application to
measure the time to initially map all the objects on the render client nodes,
and to perform a commit-sync of the full data set after mapping has been
established. All figures observe a noticable measurement jitter due to other
services running on the cluster. The details of the benchmark algorithm can be
found in the implementation~\cite{eqObjectBench}. We used the same data sets as
in the previous section. After eight processes, a node starts to run two
processes per node, which share CPU, memory and network interface bandwidth \FIXME{unclear}.

Object mapping is measured using the following settings: \textbf{none}
distributes the raw, uncompressed, and unbuffered data, \textbf{compression}
uses the Snappy compressor to distribute unbuffered data, \textbf{buffered}
reuses uncompressed, serialized data for mappings of other nodes, and
\textbf{compression buffered} compresses the buffer holding the data \FIXME{unclear}. Unbuffered operations need
to reserialize, and potentially recompress, the master object data for each
slave node. Each slave instance needs to deserialize and decompress the data.

@@

The volume data sets are distributed in a single object, serializing the
raw volume buffer. The Spike volume data set has a significant compression
ratio, which is reflected by the results in \fig{fSpikesDist}. Compression for this
data is beneficial for transmitting data over a 10~Gb/s link even for a single
slave process only (970 MB/s vs 570 MB/s raw data transfer) \FIXME{unclear}. Buffering has
little benefit since the serialization of volume data is trivial. Buffered
compression makes a significant difference, since the compression cost can be amortized
over $n$ nodes, reaching raw data transmission rates of 3.7 GB/s with the
default Snappy compressor and at best 4.4 GB/s with ZStandard at level 1.

@@

>>>>

RLE compression has a very low overhead but merely removes ``blank space'' in
the data. The Snappy compression, used as default in \textsf{Collage}, achieves
the same compression ratio as the LZ variants at a much higher speed. The
ZStandard compressor has roughly the same speed as the LZ variants at the lowest
compression level, but provides significantly better compression. At higher
compression levels it can improve the compression ratio slightly, but at a high
cost for the compression speed.

@@

In this section we analyse how data distribution and synchronization performs in
real-world applications. We extracted the existing data distribution code from a
mesh renderer (eqPly) and a volume renderer (Livre) into a benchmark application
to measure the time to initially map all the objects on the render client nodes,
and to perform a commit-sync of the full data set after mapping has been
established. All figures observe a noticable measurement jitter due to other
services running on the cluster. The details of the benchmark algorithm can be
found in the implementation~\cite{eqObjectBench}. used the same data sets as in
the previous section. We ran the benchmark on up to eight physical nodes, that
is, after eight processes nodes start to run two processes per node, which share
CPU, memory and network interface bandwidth.

Object mapping is measured using the following settings: \textbf{none}
distributes the raw, uncompressed, and unbuffered data, \textbf{compression}
uses the Snappy compressor to distribute unbuffered data, \textbf{buffered}
reuses uncompressed, serialized data for mappings from multiple nodes, and
\textbf{compression buffered} reused the compressed buffer for multiple nodes.
Unbuffered operations need to reserialize, and potentially recompress, the
master object data for each slave node. Each slave instance needs to deserialize
and decompress the data.

@@

The volume data sets are distributed in a single object, serializing the raw
volume buffer. The Spike volume data set has a significant compression ratio,
which is reflected by the results in \fig{fSpikesDist}. Compression for this
data is beneficial for transmitting data over a 10~Gb/s link even for a single
slave process only. Buffering has little benefit since the serialization of
volume data is trivial. Buffered compression makes a significant difference,
since the compression cost can be amortized over $n$ nodes, reaching raw data
transmission rates of 3.7 GB/s with the default Snappy compressor and at best
4.4 GB/s with ZStandard at level 1.

@@

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/compounds}
  \caption{\label{fCompounds}Compound scalability for polygonal and volume data}
\end{figure*}

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/equalizers}
  \caption{\label{fEqualizers}Scalability with heterogenous rendering resources}
\end{figure*}
